Analysing Constraint Grammars with a SAT solver

### 2015-10-24 paper/lrec/problem_desc.tex
eval
add examples of conflicts

As CGs grow larger, it gets harder for the grammar writers and users to keep track of all the rules and their interaction.
%\cite{voutilainen2004} gives a detailed account about best practices of grammar writing and efficient use of hand-annotated corpora to aid the grammar development.
%\cite{bick2013tuning} presents a method to optimise hand-written CGs using machine learning techniques.
%Our tools complement the existing methods in CG analysis and optimisation.
%While Bick's experiments show improvements in results, the grammar writer is none the wiser why is the grammar better.
%Authors who have a large hand-annotated corpus can also benefit from our tools.
With our tools, the users can diagnose and improve their grammars.
We can ask specific questions about a given grammar, such as:

\begin{itemize}
\item Are there rules that contradict each other?
\item Are there rules that will never fire?
\item Generate a sequence that triggers rule(s) X but not rule(s) Y
%\item Generate a sequence that is ambiguous but doesn't trigger any rules
\end{itemize}

>>>>

As CGs grow larger, it gets harder for the grammar writers and users to keep track of all the rules and their interaction.
%\cite{voutilainen2004} gives a detailed account about best practices of grammar writing and efficient use of hand-annotated corpora to aid the grammar development.
%\cite{bick2013tuning} presents a method to optimise hand-written CGs using machine learning techniques.
%Our tools complement the existing methods in CG analysis and optimisation.
%While Bick's experiments show improvements in results, the grammar writer is none the wiser why is the grammar better.
%Authors who have a large hand-annotated corpus can also benefit from our tools.
With our tools, the users can diagnose and improve their grammars.
They can ask specific questions about a given grammar, such as:

\begin{itemize}
\item Are there rules that contradict each other?
\item Are there rules that will never fire?
\item Generate a sequence that triggers rule(s) R1 but not rule(s) R2
%\item Generate a sequence that is ambiguous but doesn't trigger any rules
\end{itemize}

Some examples where a rule contradicts another are listed below. R1
can also be a set of rules: for instance, one rule removes a verb if
preceded by a determiner, and another if not preceded by a determiner,
and together these rules remove a verb in all possible cases.
\begin{enumerate}
\item If a rule appears twice, the second occurrence will be disabled by the first
\item R1 selects something in a context, R2 removes it
\item R1 removes something from R2's context, so R2 can never apply
\end{enumerate}
